|

### 2024-03-26 manuscript/manuscript.qmd
manuscript update

  Longitudinal Analysis Manuscript: Working Draft
subtitle: Longitudinal Analysis using data from the ABCD© Study

@@

code-repo: "Access the code, data, and analysis at <http://swhawes.github.io/test/>"

@@

  email: shawes@fiu.edu

@@

    department: Center for Children & Families
    city: Miami
    region: FL
    country: United States

@@

  email: andrew.littlefield@ttu.edu

@@

    department: Psychological Sciences
    city: Lubbock
    region: TX
    country: United States

@@

  email: lopdanie@ohsu.edu

@@

    department: Department of Psychiatry
    city: Portland
    region: OR
    country: United States

@@

  email: SherK@missouri.edu

@@

    department: Psychological Sciences
    city: Columbia
    region: MO
    country: United States

@@

  email: erthomps@fiu.edu

@@

  email: gonzara@fiu.edu

@@

  email: laaguinaldo@health.ucsd.edu

@@

    department: Department of Psychiatry
    city: San Diego
    region: CA
    country: United States

@@

  email: asadams@fiu.edu

@@

  email: mbayat@fiu.edu

@@

    department: Cognitive Neuorscience
    city: Miami
    region: FL
    country: United States

@@

  email: byrdal@upmc.edu

@@

    department: Department of Psychiatry
    city: Pittsburgh
    region: PA
    country: United States

@@

  email: Luis.Araujo@vcuhealth.org

@@

    department: Virginia Institute for Psychiatric and Behavioral Genetics
    city: Richmond
    region: VA
    country: United States

@@

  email: adick@fiu.edu

@@

  email: sheering@umich.edu

@@

    department: Institute for Social Research
    city: Ann Arbor
    region: MI
    country: United States

@@

  email: ckaiv001@fiu.edu

@@

  email: slehman@fiu.edu

@@

  email: lil033@ucsd.edu

@@

    department: Department of Radiology
    city: San Diego
    region: CA
    country: United States

@@

  email: jlinkersdoerfer@ucsd.edu

@@

    department: Center for Human Development
    city: San Diego
    region: CA
    country: United States

@@

  email: Thomas.Maullin-Sapey@bdi.ox.ac.uk

@@

    department: Oxford Big Data Institute
    city: Oxford
    region: UK
    country: United Kingdom

@@

  email: Michael.Neale@vcuhealth.org

@@

  email: thomas.nichols@bdi.ox.ac.uk

@@

  email: sperl@sas.upenn.edu

@@

    department: Department of Psychology
    city: Philadelphia
    region: PA
    country: United States

@@

  email: stapert@ucsd.edu

@@

  email: CEV18@pitt.edu

@@

    department: Department of Psychology
    city: Pittsburgh
    region: PA
    country: United States

@@

  email: mwagner@ucsd.edu

@@

    department: The Institute for Neural Computation
    city: San Diego
    region: CA
    country: United States

@@

  email: rwaller@sas.upenn.edu

@@

  email: wes.stat@gmail.com

@@

    department: Center for Population Neuroscience and Genetics
    city: Tulsa
    region: OK
    country: United States

>>>>

  Longitudinal Analysis of the ABCD&reg; Study

@@

code-repo: "Access the code, data, and analysis at <https://github.com/OpenDevSci/LongDev-ABCD>"

@@

  #email: shawes@fiu.edu

@@

    #department: Center for Children & Families
    #city: Miami
    #region: FL
    #country: United States

@@

  #email: andrew.littlefield@ttu.edu

@@

    #department: Psychological Sciences
    #city: Lubbock
    #region: TX
    #country: United States

@@

  #email: lopdanie@ohsu.edu

@@

    #department: #department of Psychiatry
    #city: Portland
    #region: OR
    #country: United States

@@

  #email: SherK@missouri.edu

@@

    #department: Psychological Sciences
    #city: Columbia
    #region: MO
    #country: United States

@@

  #email: erthomps@fiu.edu

@@

  #email: gonzara@fiu.edu

@@

  #email: laaguinaldo@health.ucsd.edu

@@

    #department: #department of Psychiatry
    #city: San Diego
    #region: CA
    #country: United States

@@

  #email: asadams@fiu.edu

@@

  #email: mbayat@fiu.edu

@@

    #department: Cognitive Neuorscience
    #city: Miami
    #region: FL
    #country: United States

@@

  #email: byrdal@upmc.edu

@@

    #department: #department of Psychiatry
    #city: Pittsburgh
    #region: PA
    #country: United States

@@

  #email: Luis.Araujo@vcuhealth.org

@@

    #department: Virginia Institute for Psychiatric and Behavioral Genetics
    #city: Richmond
    #region: VA
    #country: United States

@@

  #email: adick@fiu.edu

@@

  #email: sheering@umich.edu

@@

    #department: Institute for Social Research
    #city: Ann Arbor
    #region: MI
    #country: United States

@@

  #email: ckaiv001@fiu.edu

@@

  #email: slehman@fiu.edu

@@

  #email: lil033@ucsd.edu

@@

    #department: #department of Radiology
    #city: San Diego
    #region: CA
    #country: United States

@@

  #email: jlinkersdoerfer@ucsd.edu

@@

    #department: Center for Human Development
    #city: San Diego
    #region: CA
    #country: United States

@@

  #email: Thomas.Maullin-Sapey@bdi.ox.ac.uk

@@

    #department: Oxford Big Data Institute
    #city: Oxford
    #region: UK
    #country: United Kingdom

@@

  #email: Michael.Neale@vcuhealth.org

@@

  #email: thomas.nichols@bdi.ox.ac.uk

@@

  #email: sperl@sas.upenn.edu

@@

    #department: #department of Psychology
    #city: Philadelphia
    #region: PA
    #country: United States

@@

  #email: stapert@ucsd.edu

@@

  #email: CEV18@pitt.edu

@@

    #department: #department of Psychology
    #city: Pittsburgh
    #region: PA
    #country: United States

@@

  #email: mwagner@ucsd.edu

@@

    #department: The Institute for Neural Computation
    #city: San Diego
    #region: CA
    #country: United States

@@

  #email: rwaller@sas.upenn.edu

@@

  #email: wes.stat@gmail.com

@@

    #department: Center for Population Neuroscience and Genetics
    #city: Tulsa
    #region: OK
    #country: United States
